---
title: "Preprocessing"
author: "Kiri Kuroda"
output:
  html_document:
    theme: flatly
    includes:
      in_header: ../html/header.html
    css: ../css/style.css
    md_extensions: -ascii_identifiers
    df_print: paged
    chunk_output_type: console
    toc: yes
    toc_float:
      collapsed: false
---

<br>

# Setup

Load packages and functions.

```{r setup, message=FALSE}
library(tidyverse)
library(qualtRics)

# User-defined functions
source("../function/r/my_functions.R")
```

<br>

# Preprocessing

Bind the individual files to one csv file, and save it in `../data/preprocessed`. `bind_rawdata()` is defined in `../function/r/my_functions.R`.

```{r, message=FALSE, eval=FALSE}
bind_rawdata(c("gamble", "solo", "solo_gabor", "group", "group_gabor"))
```

<br>

Preprocess the raw questionnaire data, and make a new file (`../data/preprocessed/questionnaire.csv`). For details of social-value-orientation (SVO) scoring and the items, see Ryan O. Murphy's website (http://ryanomurphy.com).

```{r, message=FALSE, eval=FALSE}
svo_payoff <- read_csv("../data/questionnaire/svo_payoff.csv")

read_survey("../data/questionnaire/raw_questionnaire.csv") %>%
  # Cut unnecessary columns
  select(difficulty:id) %>%
  # SVO and other data is processed below
  pivot_longer(cols = svo_1:svo_6, names_to = "item", values_to = "value") %>%
  left_join(svo_payoff, by = c("item", "value")) %>%
  mutate(self = self - 500, other = other - 500) %>%
  group_by(id) %>%
  mutate(mean_self = mean(self), mean_other = mean(other)) %>%
  filter(item == "svo_1") %>%
  mutate(
    ratio = mean_other / mean_self,
    angle = atan(ratio),
    svo_score = angle * 180 / pi,
    svo = case_when(
      svo_score > 57.15 ~ "altruist",
      svo_score > 22.45 & svo_score <= 57.15 ~ "prosocial",
      svo_score > -12.04 & svo_score <= 22.45 ~ "individualist",
      svo_score <= -12.04 ~ "competitor"
    ),
    gender = case_when(
      gender == 1 ~ "man",
      gender == 2 ~ "woman",
      gender == 3 ~ "other",
      gender == 4 ~ "noresponse"
    ),
    vision = case_when(
      vision == 1 ~ "unaided",
      vision == 2 ~ "glasses",
      vision == 3 ~ "contact",
      vision == 4 ~ "other"
    ),
    hand = if_else(hand == 1, "left", "right")
  ) %>%
  # Cut unnecessary columns and output the preprocessed data
  select(id, difficulty:hand, svo_score, svo) %>%
  arrange(id) %>%
  write_csv("../data/preprocessed/questionnaire.csv")
```

<br>

# Participants

Sixty-three students at the University of Tokyo participated in the experiment. We first checked participants' basic data.

```{r, message=FALSE}
df_questionnaire <- read_csv("../data/preprocessed/questionnaire.csv")
```

<br>

## Gender

```{r}
df_questionnaire %>%
  count(gender)
```

<br>

## Age

```{r}
df_questionnaire %>%
  summarise(
    mean_age = round(mean(age), 1),
    sd_age = round(sd(age), 1),
    min_age = min(age),
    max_age = max(age)
  )
```

<br>

## Dominant hand

```{r}
df_questionnaire %>%
  count(hand)
```

<br>

# Post-session questionnaire

Participants answered the seven items on a 7-point scale, but we do not report the results in this paper.

- `difficulty`: Rating of the task difficulty (1: *Very easy*; 7: *Very difficult*).

- `easy_other`: How much participants thought that previous 24 participants had answered correctly when the task was easy (1: *Not at all*; 7: *Very strongly*).

- `hard_other`: How much participants thought that previous 24 participants had answered correctly when the task was difficult (1: *Not at all*; 7: *Very strongly*).

- `influence`: How much participants thought that their own vote affected the majority's accuracy (1: *Not at all*; 7: *Very strongly*).

- `variety`: How much participants thought that the majority's accuracy depended on who voters were (1: *Not at all*; 7: *Very strongly*).

- `worsen`: How much participants thought that their own vote worsened the majority's accuracy (1: *Not at all*; 7: *Very strongly*).

- `improve`: How much participants thought that their own vote improved the majority's accuracy (1: *Not at all*; 7: *Very strongly*).
