---
title: "Voting and the performance of majorities"
author: "Kiri Kuroda"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    includes:
      in_header: ../html/header.html
    css: ../css/style.css
    md_extensions: -ascii_identifiers
    df_print: paged
    chunk_output_type: console
    toc: yes
    toc_float:
      collapsed: false
---

<br>

# Setup

```{r setup, message=FALSE}
library(tidyverse)
library(magrittr)
library(cmdstanr)
library(shinystan)
library(tidybayes)
library(ggridges)
library(colorspace)
library(furrr)
plan(multisession)

# User-defined functions
source("../function/r/my_functions.R")

# Import data
# We modified a column name because we realized that
# "block" sounds more intuitive than "task" in description of the analysis
df_solo <- read_csv("../data/preprocessed/solo.csv") %>%
  rename(block = task)
df_group <- read_csv("../data/preprocessed/group.csv") %>%
  rename(block = task)
df_solo_group <- bind_rows(df_solo, df_group)
df_questionnaire <- read_csv("../data/preprocessed/questionnaire.csv")

# Import the fitting results
median_powutil <- readRDS("../output/data/gamble/median_powutil.rds")
median_gabor <- readRDS("../output/data/gabor/median_gabor.rds")
median_goldstein <- readRDS("../output/data/confidence/subjective_accuracy/median_goldstein.rds")

# cmdstanr
# install_cmdstan(version = "2.28.0")
```

<br>

# Voting rate

Not surprisingly, the voting rate decreased along with the reward of the exit option.

```{r, message=FALSE}
df_group %>%
  filter(order == "post") %>%
  mutate(ori_var = factor(ori_var)) %>%
  group_by(id, ori_var, payoff_solo) %>%
  summarise(ind_mean = mean(choice == "group")) %>%
  group_by(ori_var, payoff_solo) %>%
  summarise(mean = mean(ind_mean), se = se(ind_mean)) %>%
  ggplot(aes(x = payoff_solo, y = mean, color = ori_var)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 10) +
  scale_x_continuous(labels = scales::comma) +
  scale_color_viridis_d() +
  labs(
    x = "Reward of the exit option (JPY)",
    y = "Voting rate",
    color = "Variance of orientations"
  ) +
  theme(legend.position = "top")
```

<br>

## Mixed logistic regression

We performed a mixed logistic regression predicting the voting rate from individual and task parameters.

```{r, eval=FALSE}
model_voting <- cmdstan_model("../function/stan/group/voting_logistic.stan")

datalist_logistic <- df_group %>%
  filter(order == "post") %>%
  left_join(
    median_powutil %>%
      mutate(scaled_rho = c(scale(rho))),
    by = "id"
  ) %>%
  left_join(
    median_gabor %>%
      mutate(
        scaled_gamma = c(scale(gamma)),
        scaled_lambda = c(scale(lambda))
      ),
    by = "id"
  ) %>%
  left_join(
    median_goldstein %>%
      mutate(scaled_confidence = c(scale(q_area_under_p))),
    by = "id"
  ) %>%
  mutate(
    payoff_solo = payoff_solo + payoff_jitter,
    scaled_reward = c(scale(payoff_solo)),
    scaled_var = c(scale(ori_var)),
  ) %$%
  list(
    N = nrow(.),
    N_subj = length(levels(factor(id))),
    id = id,
    choice = as.numeric(choice == "solo"),
    scaled_reward = scaled_reward,
    scaled_var = scaled_var,
    theta_var = ori_var,
    scaled_rho = scaled_rho,
    scaled_gamma = scaled_gamma,
    scaled_lambda = scaled_lambda,
    scaled_confidence = scaled_confidence
  )

fit_voting <- model_voting$sample(
  datalist_logistic, seed = 1, refresh = 100,
  chains = 4, iter_warmup = 500, iter_sampling = 2000
)

fit_voting_rstan <- cmdstan2rstan(fit_voting)
```

```{r, include=FALSE, eval=FALSE}
# fit_voting$save_output_files("../output/data/group/")
# saveRDS(fit_voting, "../output/data/group/fit_voting.rds")
# saveRDS(fit_voting_rstan, "../output/data/group/fit_voting_rstan.rds")
```

```{r, include=FALSE}
fit_voting <- readRDS("../output/data/group/fit_voting.rds")
# fit_voting_rstan <- readRDS("../output/data/group/fit_voting_rstan.rds")
```

```{r, eval=FALSE}
launch_shinystan(fit_voting_rstan)
```

<br>

## Estimates {.tabset}

Even when we controlled for the task parameters, the confidence parameter promoted participants to exit from the group. Risk preference and competence had positive effects on the exit rate, but the posterior probability was lower than 95%.

```{r}
fit_voting %>%
  spread_draws(coef_rho, coef_gamma, coef_confidence) %>%
  pivot_longer(
    cols = starts_with("coef_"),
    names_to = "param",
    values_to = "value"
  ) %>%
  ggplot(aes(x = value, y = param)) +
  stat_pointinterval(
    .width = 0.95, color = lighten("#00215d", 0.4), size = 2.5,
  ) +
  stat_pointinterval(
    .width = 0.8, color = lighten("#00215d", 0.2), size = 5
  ) +
  stat_pointinterval(
    .width = 0.5, color = "#00215d", interval_size = 10
  ) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_y_discrete(labels = c("Confidence", "Competence", "Risk preference")) +
  labs(x = "Coefficients", y = "Predictors") +
  theme(axis.text.y = element_text(hjust = 0))
```

<br>

Coefficients for the task parameters are shown below.

### Intercept

```{r}
fit_voting %>%
  spread_draws(intercept[id]) %>%
  median_qi() %>%
  arrange(intercept) %>%
  mutate(yaxis_num = row_number()) %>%
  ggplot(aes(intercept, yaxis_num)) +
  geom_point() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_y_continuous(breaks = c(seq(10, 60, 10))) +
  labs(x = "Intercept", y = "Participants")
```

<br>

### Coefficients for the reward

```{r}
fit_voting %>%
  spread_draws(coef_reward[id]) %>%
  median_qi() %>%
  arrange(coef_reward) %>%
  mutate(yaxis_num = row_number()) %>%
  ggplot(aes(coef_reward, yaxis_num)) +
  geom_point() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_y_continuous(breaks = c(seq(10, 60, 10))) +
  labs(x = "Coefficients for the reward", y = "Participants")
```

<br>

### Coefficients for the variance of orientations

```{r}
fit_voting %>%
  spread_draws(coef_var[id]) %>%
  median_qi() %>%
  arrange(coef_var) %>%
  mutate(yaxis_num = row_number()) %>%
  ggplot(aes(coef_var, yaxis_num)) +
  geom_point() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_y_continuous(breaks = c(seq(10, 60, 10))) +
  labs(x = "Coefficients for the variance", y = "Participants")
```

<br>

## Posterior predictive checking

```{r, message=FALSE}
fit_voting %>%
  spread_draws(y_pred[id][ori_var]) %>%
  sample_draws(ndraws = 20, seed = 1) %>%
  ungroup() %>%
  mutate(
    n_exit = y_pred,
    draw = factor(.draw),
    ori_var = case_when(
      ori_var == 1 ~ 8,
      ori_var == 2 ~ 16,
      ori_var == 3 ~ 32,
      ori_var == 4 ~ 64
    )
  ) %>%
  ggplot(aes(n_exit, ..density..)) +
  geom_line(aes(group = draw), stat = "density", color = "gray", size = 0.5) +
  geom_line(
    data = df_group %>%
      filter(order == "post") %>%
      group_by(id, ori_var) %>%
      summarise(n_exit = sum(choice == "solo")),
    stat = "density", color = "#009E73", size = 2
  ) +
  facet_wrap(vars(ori_var)) +
  labs(x = "Choice frequency of the solo option", y = "Density") +
  theme_facet +
  theme(legend.position = "top")
```

<br>

# Actual majority accuracy

We calculated the actual accuracy of majority by sampling the votes 10000 times. We discarded the runs in which no participant had voted.

```{r, eval=FALSE}
sim_actual_voting <- 1:10000 %>%
  future_imap_dfr(~{
    tmp <- df_group %>%
      group_by(id, ori_var, payoff_solo) %>%
      sample_n(1) %>%
      group_by(ori_var, payoff_solo) %>%
      sample_n(25) %>%
      summarise(
        n_group = sum(choice == "group"),
        n_solo = sum(choice == "solo"),
        n_group_correct = sum(choice == "group" & result == "correct"),
        n_solo_correct = sum(choice == "solo" & result == "correct"),
        .groups = "drop"
      ) %>%
      rowwise() %>%
      mutate(
        result_group = case_when(
          n_group == 0 ~ "abort",
          n_group_correct > n_group / 2 ~ "correct",
          n_group_correct < n_group / 2 ~ "wrong",
          n_group_correct == n_group / 2 ~ sample(c("correct", "wrong"), 1)
        ),
        accuracy_solo = n_solo_correct / n_solo,
        sim_id = .y
      )
    },
    .options = furrr_options(seed = 1)
  )
```

```{r, include=FALSE, eval=FALSE}
# saveRDS(sim_actual_voting, "../output/data/group/sim_actual_voting.rds")
```

```{r, include=FALSE}
sim_actual_voting <- readRDS("../output/data/group/sim_actual_voting.rds")
```

<br>

```{r}
sim_actual_voting %>%
  group_by(ori_var, payoff_solo) %>%
  summarise(mean = mean(accuracy_solo, na.rm = TRUE)) %>%
  ggplot(aes(payoff_solo, mean)) +
  geom_point() +
  geom_line() +
  facet_wrap(vars(ori_var))
```


```{r}
sim_actual_voting %>%
  filter(result_group != "abort") %>%
  group_by(ori_var, payoff_solo) %>%
  summarise(mean = mean(result_group == "correct")) %>%
  ggplot(aes(payoff_solo, mean)) +
  geom_line() +
  facet_wrap(vars(ori_var))
```


<br>

# Group-size

```{r, eval=FALSE}
sim_condorcet_voting <- 1:10000 %>%
  future_imap_dfr(~{
    1:25 %>%
      future_map_dfr(~{
        df_group %>%
          filter(order == "post") %>%
          group_by(id, ori_var) %>%
          slice_sample(n = 1) %>%
          group_by(ori_var) %>%
          slice_sample(n = .x) %>%
          summarise(
            n_group = n(),
            n_group_correct = sum(result == "correct"),
            .groups = "drop"
          ) %>%
          rowwise() %>%
          mutate(
            result_group = case_when(
              n_group_correct > n_group / 2 ~ "correct",
              n_group_correct < n_group / 2 ~ "wrong",
              n_group_correct == n_group / 2 ~ sample(c("correct", "wrong"), 1)
            )
          )
        },
        .options = furrr_options(seed = .y)
      ) %>%
      mutate(sim_id = .y, group = "condorcet")
    },
    .options = furrr_options(seed = 1)
  )
```

```{r, eval=FALSE}
sim_k_voting <- 1:10000 %>%
  future_imap_dfr(~{
    1:25 %>%
      future_map_dfr(~{
        df_group %>%
          filter(order == "post" & choice == "group") %>%
          group_by(id, ori_var) %>%
          slice_sample(n = 1) %>%
          group_by(ori_var) %>%
          slice_sample(n = .x) %>%
          group_by(ori_var) %>%
          summarise(
            n_group = n(),
            n_group_correct = sum(result == "correct"),
            .groups = "drop"
          ) %>%
          rowwise() %>%
          mutate(
            result_group = case_when(
              n_group_correct > n_group / 2 ~ "correct",
              n_group_correct < n_group / 2 ~ "wrong",
              n_group_correct == n_group / 2 ~ sample(c("correct", "wrong"), 1)
            )
          )
        },
        .options = furrr_options(seed = .y)
      ) %>%
      mutate(sim_id = .y, group = "real")
    },
    .options = furrr_options(seed = 1)
  )
```

```{r, eval=FALSE}
sim_groupsize_voting <- bind_rows(sim_condorcet_voting, sim_k_voting)
```

```{r}
# saveRDS(sim_condorcet_voting, "../output/data/group/sim_condorcet_voting.rds")
# saveRDS(sim_k_voting, "../output/data/group/sim_k_voting.rds")
# saveRDS(sim_groupsize_voting, "../output/data/group/sim_groupsize_voting.rds")
```

```{r, include=FALSE}
sim_condorcet_voting <- readRDS("../output/data/group/sim_condorcet_voting.rds")
sim_k_voting <- readRDS("../output/data/group/sim_k_voting.rds")
sim_groupsize_voting <- readRDS("../output/data/group/sim_condorcet_voting.rds")
```

```{r}
sim_forced_voting <- 1:10000 %>%
  future_imap_dfr(~{
    tmp <- df_group %>%
      group_by(id, ori_var) %>%
      sample_n(1) %>%
      group_by(ori_var) %>%
      sample_n(25) %>%
      summarise(
        n_correct = sum(result == "correct"),
        .groups = "drop"
      ) %>%
      mutate(
        result_group = if_else(n_correct >= 13, "correct", "wrong"),
        sim_id = .y
      )
    },
    .options = furrr_options(seed = 1)
  )
```


```{r}
saveRDS(sim_forced_voting, "../output/data/group/sim_forced_voting.rds")
```



```{r}
tibble(a=1:4) %>%
  sample_n(sum(a == 2), )
```

```{r}
df_group %>%
  group_by(id, ori_var, payoff_solo) %>%
  slice_sample(n = 1) %>%
  group_by(ori_var, payoff_solo) %>%
  slice_sample(n = 25) %>%
  mutate(n_group = sum(choice == "group")) %>%
  filter(row_number() <= n_group)
```

```{r, eval=FALSE}
sim_nobias_voting <- 1:10000 %>%
  future_imap_dfr(~{
    tmp <- df_group %>%
      group_by(id, ori_var, payoff_solo) %>%
      slice_sample(n = 1) %>%
      group_by(ori_var, payoff_solo) %>%
      slice_sample(n = 25) %>%
      mutate(n_group = sum(choice == "group")) %>%
      filter(row_number() <= n_group) %>%
      summarise(
        n_group = n(),
        n_group_correct = sum(result == "correct"),
        .groups = "drop"
      ) %>%
      rowwise() %>%
      mutate(
        result_group = case_when(
          n_group == 0 ~ "abort",
          n_group_correct > n_group / 2 ~ "correct",
          n_group_correct < n_group / 2 ~ "wrong",
          n_group_correct == n_group / 2 ~ sample(c("correct", "wrong"), 1)
        ),
        sim_id = .y
      )
    },
    .options = furrr_options(seed = 1)
  )
```

```{r}
saveRDS(sim_nobias_voting, "../output/data/group/sim_nobias_voting.rds")
```

```{r}
sim_nobias_voting <- readRDS("../output/data/group/sim_nobias_voting.rds")
```


```{r}
sim_nobias_voting %>%
  group_by(ori_var, payoff_solo) %>%
  summarise(mean = mean(result_group == "correct")) %>%
  ggplot(aes(payoff_solo, mean)) +
  geom_line() +
  facet_wrap(vars(ori_var))
```

